Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2020-12-30 vesicle_code/docs/permeableVes/main.tex
yny

\begin{abstract}
In this work we use boundary integral simulations to investigate the
effects of water permeability on the hydrodynamics of a vesicle under
various flows and confinement configurations. Using the Helfrich free
energy extended for the coupling of membrane permeability with the
membrane elastic stress, tension and mechanical stress, we illustrate
that, in the absence of an osmotic stress gradient, a typical liposome
may be significantly affected by membrane permeability over a
sufficiently long time or under strong confinement. Lipid bilayer
membranes are permeable to water molecules, and water influx/efflux is
often assumed to be negligible in the absence of osmolarity, even when
the membrane undergoes large deformation. Our simulation results
quantify the conditions for such assumption to be valid, and shed
light on how confinement can be utilized to estimate membrane
permeability.
%
%osmotic stress gradient 
%We describe a mathematical model for a semipermeable vesicle and derive
%  a boundary integral equation formulation for simulating its
%  hydrodynamics.  
%
%Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

@@

At the beginning of the simulations a semipermeable vesicle is
initialized above the center line $y=0$, and it migrates towards the
center line as in the impermeable case~\cite{dan-vla-mis2009}. 
%
%However,
%for an impermeable vesicle, depending on the initial reduced area and
%the maximum flow velocity $U$, the equilibrium vesicle shape is either
%an axisymmetric parachute or bullet, or an asymmetric tank-treading
%slipper~\cite{kao-bir-mis2009}. 
%
%To validate our methods,
%in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
%for the steady state shape of an impermeable vesicle
%vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
%qualitatively agree, Kaoui et al.~report that the vesicles with
%$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
%axisymmetric. In our simulations these vesicles are slightly asymmetric,
%are undergoing a tank treading motion, and we therefore report them as
%asymmetric slippers.
%
Using several initial reduced areas and flow rates, we recreate the
impermeable vesicle phase diagram for vesicles with a permeability rate
of $\beta = 10^{-3}$. The equilibrium vesicle shape for different $U$
and initial reduced area is summarized in
Figure~\ref{fig:parabolicComposite}(a), and the vertical displacement of
the vesicle's center of mass is in
Figure~\ref{fig:parabolicComposite}(b). The effect of semipermeability
of a vesicle with $alpha(0) = 0.9$ and $U=800 \mu$m/s on its reduced
area and migration pattern are shown in
Figure~\ref{fig:parabolicComposite}(c) and (d). 
%

@@

The two phases in the relaxation dynamics are also observed  in the hydrodynamics of a semipermeable vesicle under a shear flow (both the planar and Poiseuille flows) in free space. 
As an impermeable vesicle in a shear flow, a semipermeable vesicle also reaches an equilibrium shape and position. Yet for a semipermeable vesicle the equilibrium shape depends on the strength of the shear flow (shear rate $\dot\gamma$ for the planar shear flow, and $U_{max}$ for the Poiseuille flow). Our simulations also show that, in a Poiseuille flow, symmetric equilibrium vesicle shape is possible only at low flow velocity. In experiments it may take a few hours for the semipermeable vesicle to reach such  equilibria that could be used to quantify the flow strength.

>>>>

\begin{abstract}
Lipid bilayer membranes have a native (albeit small) permeability for water molecules. 
As long as the bilayer structure stays intact without poration or rupture under load, 
the water influx/efflux  is
often assumed to be negligible in the absence of a gradient of osmotic stress. 
In this work we use boundary integral simulations to investigate the
effects of water permeability on the hydrodynamics of a vesicle under
various flows and confinement configurations. Coupling the membrane permeability with membrane elastic stress, tension and mechanical stress 
in the framework of Helfrich free energy, we illustrate
that, in the absence of an osmotic stress gradient, a giant unilamellar vesicle may be significantly affected by water influx/efflux over a
sufficiently long time or under a strong confinement. 
Our simulation results quantify the conditions for water permeation to be negligible in terms of the timescales, flow strength of an external flow, and degree of confinement.
These results shed light on how microfluidic confinement can be utilized to estimate membrane permeability.
%
%osmotic stress gradient 
%We describe a mathematical model for a semipermeable vesicle and derive
%  a boundary integral equation formulation for simulating its
%  hydrodynamics.  
%
%Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

@@

At the beginning of the simulations a semipermeable vesicle is
initialized above the center line $y=0$, and it migrates towards the
center line as in the impermeable case~\cite{dan-vla-mis2009}. 
%
%However,
%for an impermeable vesicle, depending on the initial reduced area and
%the maximum flow velocity $U$, the equilibrium vesicle shape is either
%an axisymmetric parachute or bullet, or an asymmetric tank-treading
%slipper~\cite{kao-bir-mis2009}. 
%
%To validate our methods,
%in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
%for the steady state shape of an impermeable vesicle
%vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
%qualitatively agree, Kaoui et al.~report that the vesicles with
%$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
%axisymmetric. In our simulations these vesicles are slightly asymmetric,
%are undergoing a tank treading motion, and we therefore report them as
%asymmetric slippers.
%
Using several initial reduced areas and flow rates, we recreate the
impermeable vesicle phase diagram for vesicles with a permeability rate
of $\beta = 10^{-3}$. The equilibrium vesicle shape for different $U$
and initial reduced area is summarized in
Figure~\ref{fig:parabolicComposite}(a), and the vertical displacement of
the vesicle's center of mass is in
Figure~\ref{fig:parabolicComposite}(b). The effect of semipermeability
of a vesicle with $\alpha(0) = 0.9$ and $U=800 \mu$m/s on its reduced
area and migration pattern are shown in
Figure~\ref{fig:parabolicComposite}(c) and (d). 
%

@@

The two phases in the relaxation dynamics are also observed  in the hydrodynamics of a semipermeable vesicle under a shear flow (both the planar and Poiseuille flows) in free space. 
Similar to an impermeable vesicle in a shear flow, a semipermeable vesicle also reaches an equilibrium shape and position. Yet for a semipermeable vesicle the equilibrium shape depends on the strength of the shear flow (shear rate $\dot\gamma$ for the planar shear flow, and $U_{max}$ for the Poiseuille flow). Our simulations also show that, in a Poiseuille flow, symmetric equilibrium vesicle shape is possible only at low flow velocity. In experiments it may take a few hours for the semipermeable vesicle to reach such equilibria that could be used to quantify the flow strength.
